Life in the canopy: Community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-01-28 ms/manuscript.Rmd
Revise MS as per submission V2

```{r word-count table}
tibble(
  words = c(
    "Total word count (Introduction, Materials and Methods, Results, Discussion):_6498",
    "Summary:_199",
    "Introduction:_881",
    "Materials and Methods:_2410",
    "Results:_798",
    "Discussion:_2409",
    "Acknowledgements:_170"),
  figs_tabs = c(
    "No. of figures:_7 (all in color)",
    "No. of tables:_5",
    "No. of supporting information files:_8 (Figs. S1-S2; Tables S1-S6)", "", "", "", "")
) %>%
  separate(words, c("words", "word_count"), sep = "_") %>%
  separate(figs_tabs, c("figs", "fig_count"), sep = "_", fill = "right") %>%
  mutate_all(~replace_na(., "")) %>%
  knitr::kable(format = "latex", escape = TRUE, col.names = NULL) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "12em") %>%
  column_spec(2, width = "2em") %>%
  column_spec(3, width = "12em") %>%
  column_spec(4, width = "8em")
```

@@

### The dual roles of the canopy as both a filter and promoter of diversity

@@

Recent studies [\eg, @Sundue2015; @Testo2016a; @Lehtonen2017; @Testo2018a] have called into question the scenario of rapid Cretaceous radiations of epiphytic ferns posited by @Schuettpelz2009 by failing to detect increased rates of diversification associated with epiphytic growth.
Our study provides a fresh perspective on this issue. 
Here, we demonstrate that epiphytism is likely a complex trait, and almost certainly requires the evolution of multiple associated and dependent traits. 
We propose that the timing and order of the evolution of such traits are related to the conflicting diversification dynamics observed in these studies.
Another possibility raised by our results is that fern epiphytes have radiated morphologically without corresponding species-level diversification [@Givnish2015].
Future research investigating the tempo and mode of the evolution of epiphytism in ferns should seek to better partition this functional diversity when exploring hypotheses of exceptional species diversification.

>>>>

```{r word-count table}
tibble(
  words = c(
    "Total word count (Introduction, Materials and Methods, Results, Discussion):_6499",
    "Summary:_199",
    "Introduction:_881",
    "Materials and Methods:_2410",
    "Results:_798",
    "Discussion:_2410",
    "Acknowledgements:_170"),
  figs_tabs = c(
    "No. of figures:_7 (all in color)",
    "No. of tables:_5",
    "No. of supporting information files:_8 (Figs. S1-S2; Tables S1-S6)", "", "", "", "")
) %>%
  separate(words, c("words", "word_count"), sep = "_") %>%
  separate(figs_tabs, c("figs", "fig_count"), sep = "_", fill = "right") %>%
  mutate_all(~replace_na(., "")) %>%
  knitr::kable(format = "latex", escape = TRUE, col.names = NULL) %>%
  kable_styling(full_width = FALSE) %>%
  column_spec(1, width = "12em") %>%
  column_spec(2, width = "2em") %>%
  column_spec(3, width = "12em") %>%
  column_spec(4, width = "8em")
```

@@

### The dual roles of the canopy as both a filter and promoter of community diversity

@@

Recent studies [\eg, @Sundue2015; @Testo2016a; @Lehtonen2017; @Testo2018a] have called into question the scenario of rapid Cretaceous radiations of epiphytic ferns posited by @Schuettpelz2009 by failing to detect increased rates of diversification associated with epiphytic growth.
Our study provides a fresh perspective on this issue. 
Here, we demonstrate that epiphytism is likely a complex trait, and almost certainly requires the evolution of multiple associated and dependent traits. 
We propose that the timing and order of the evolution of such traits are related to the conflicting diversification dynamics observed in these studies.
Another possibility raised by our results is that fern epiphytes have radiated morphologically without corresponding species-level diversification [@Givnish2015].
Future research investigating the tempo and mode of the evolution of epiphytism in ferns should seek to better partition this morphological diversity when exploring hypotheses of exceptional species diversification.
